COFFEE: an Optimizing Compiler\\for Finite Element Local Assembly

### 2014-04-03 paper/bare_conf.tex
Minor fixes

\begin{abstract}
%\boldmath
The numerical solution of partial differential equations using the finite element method is a key application in scientifc computing. Local assembly is its characteristic operation, which executes a problem-specific kernel for each element in the discretized problem domain. Since the domain size can be huge, executing efficient kernels is fundamental. Their optimization is, however, a challenging issue. Even though affine loop nests are generally present, the short trip counts and the complexity of mathematical expressions make it hard to determine a single or unique sequence of successful transformations. We present the design and systematic evaluation of COFFEE, a domain-specific compiler for local assembly kernels. COFFEE manipulates abstract syntax trees by introducing composable optimizations aimed at improving instruction-level parallelism, especially SIMD vectorization, and register locality. It then generates C code including vector intrinsics. Experiments using a suite of real-world examples show that significant performance improvement is achieved.
\end{abstract}

>>>>

\begin{abstract}
%\boldmath
Numerical solution of partial differential equations using the finite element method is one of the key applications of high performance computing. The local assembly is its characteristic operation, which executes a problem-specific kernel for each element in the discretized problem domain. Since the domain size can be huge, executing efficient kernels is fundamental. Their optimization is, however, a challenging issue. Even though affine loop nests are generally present, the short trip counts and the complexity of mathematical expressions make it hard to determine a single or unique sequence of successful transformations. We present, therefore, the design and systematic evaluation of COFFEE, a domain-specific compiler for local assembly kernels. COFFEE manipulates abstract syntax trees by introducing composable optimizations aimed at improving instruction-level parallelism, especially SIMD vectorization, and register locality. It then generates C code including vector intrinsics. Experiments using a suite of real-world examples show that significant performance improvement is achieved.
\end{abstract}
